Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-20 cloneoverflow-latex/cloneoverflow.tex
Added another stats in RQ1 without the false positive (AC pairs).
Added the manually confirmed data sets.

The number of online clone pairs reported by running Simian and NiCad
are presented in \Cref{tab:raw_stats}. $S_D$ reports 67,570 clone
pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report
much larger numbers of clone pairs, 63,635,844 and 251,449,849 pairs
respectively. This is expected since EvaClone configurations prefer
recall~\cite{Wang2013}.  The average clone size reported by $S_D$ is
9.11 lines which is bigger than for $S_E$ (5.95 lines). Similarly,
$N_D$ has an average clone size of 10.85 lines which is bigger than
6.28 lines reported by $N_E$. The drop in size is due to the EvaClone
configuration with a smaller minimum size (\Cref{t:param_tuning}).

@@

\begin{table}
	\centering
	\caption{Statistics of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
	\label{tab:raw_stats}
	%\small
	%\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r}
			\hline
			Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
			\hline
			Stack Overflow Snippets & 1,086 & 1,531 & 1,392 & 12,886 \\
			No. of Qualitas projects & 92 & 111 & 82 & 88 \\
%			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
%			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
%			Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
			Avg.~C$_{\textrm{\textit{\%}}}$ & 38\% & 50\% & 30\% & 33\% \\
			\hline
		\end{tabular} %
	%}
\end{table}

@@

The statistics on clones obtained from running Simian and NiCad are
presented in \Cref{tab:raw_stats}. Simian in the default configuration
($S_D$) reported clones in 1,086 snippets, approximately 1\% of the
144,064 Stack Overflow snippets, associated with 92 Qualitas
projects. Simian in the EvaClone configuration ($S_E$) reported 1,531
snippets containing clones associated with all 111 Qualitas
projects. NiCad in the default configuration ($N_D$) reported clones
between 1,392 Stack Overflow code snippets and 82 Qualitas
projects. NiCad in the EvaClone configuration ($N_E$) reported the
largest number of 12,886 cloned snippets mainly due to the more
relaxed configuration. The $N_E$ snippets are associated with 88
Qualitas projects.  For the cloned Stack Overflow snippets, the
average ratio of cloned code for $S_D$, $S_E$, $N_D$, and $N_E$ is
38\%, 50\%, 30\%, and 33\% respectively.
% A quick manual check of Simian's clone report revealed that there
% were 11 problematic snippets. These 11 snippets triggered Simian to
% generate large clone clusters containing a huge number of false
% clones from array initialisation. Hence, their clones were removed
% from further analyses.

@@

\begin{table}
\caption{Investigated online clone pairs and snippets \FIXME{maybe
    merge with tables 7 and/or 9}}
\label{tab:snippets}
\centering
\begin{tabular}{l|rrrr}
  & Pairs & Snippets & Projects & Avg.~C$_{\textrm{\textit{\%}}}$ \\
\hline
\textit{good} & 2,308 & 92 & 66 & \\
\textit{ok'} & 11,749 & 136 & 39 & \\
$S_D'$ & 17,081 & 471 & 76 & \\
$N_D'$ & 88 & 77 & 29 & \\
\hline
Total & 31,946 & 621 & 95 &
\end{tabular}
\end{table}

However, using Bellon's criteria for matching clone pairs, only
0.1\textperthousand~of all pairs are agreed by two tool/configuration
combinations. As shown in \Cref{tab:snippets}, for the 2,308
\textit{good} pairs, there are 92 Stack Overflow snippets which are
associated with 66 Qualitas projects. The 11,749 \textit{ok'} pairs
are clones between 136 Stack Overflow snippets and 39 Qualitas
projects.  Moreover, for the disagreed pairs, we found 17,081 clone
pairs reported by $S_D'$ are clones between 471 Stack Overflow
snippets and 76 Qualitas projects and 88 $N_D'$ clone pairs are clones
between 77 Stack Overflow snippets and 29 Qualitas projects. In total
we found that the manually investigated 31,946 clones pairs are clones
between 621 Stack Overflow snippets and 95 Qualitas projects.

\textbf{To answer RQ1, we found most Qualitas projects to share
  similar code with Stack Overflow code snippets. Depending on the
  data set, between 82 to all 111 projects share similar code. This
  holds even for the investigated data set where 95 projects share
  code with Stack Overflow.}

>>>>

The number of online clone pairs reported by running Simian and NiCad
are presented in \Cref{tab:orig_stats}. $S_D$ reports 67,570 clone
pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report
much larger numbers of clone pairs, 63,635,844 and 251,449,849 pairs
respectively. This is expected since EvaClone configurations prefer
recall~\cite{Wang2013}.  The average clone size reported by $S_D$ is
9.11 lines which is bigger than for $S_E$ (5.95 lines). Similarly,
$N_D$ has an average clone size of 10.85 lines which is bigger than
6.28 lines reported by $N_E$. The drop in size is due to the EvaClone
configuration with a smaller minimum size (\Cref{t:param_tuning}).

@@

% \begin{table}
% 	\centering
% 	\caption{Statistics of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
% 	\label{tab:raw_stats}
% 	%\small
% 	%\resizebox{\columnwidth}{!}{%
% 		\begin{tabular}{l|r|r|r|r}
% 			\hline
% 			Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
% 			\hline
% 			Stack Overflow Snippets & 1,086 & 1,531 & 1,392 & 12,886 \\
% 			No. of Qualitas projects & 92 & 111 & 82 & 88 \\
% %			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
% %			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
% %			Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
% 			Avg.~C$_{\textrm{\textit{\%}}}$ & 38\% & 50\% & 30\% & 33\% \\
% 			\hline
% 		\end{tabular} %
% 	%}
% \end{table}

@@

The statistics on clones obtained from the different data sets are
presented in \Cref{tab:snippets}. Simian in the default configuration
($S_D$) reported clones in 1,086 snippets, approximately 1\% of the
144,064 Stack Overflow snippets, associated with 92 Qualitas
projects. Simian in the EvaClone configuration ($S_E$) reported 1,531
snippets containing clones associated with all 111 Qualitas
projects. NiCad in the default configuration ($N_D$) reported clones
between 1,392 Stack Overflow code snippets and 82 Qualitas
projects. NiCad in the EvaClone configuration ($N_E$) reported the
largest number of 12,886 cloned snippets mainly due to the more
relaxed configuration. The $N_E$ snippets are associated with 88
Qualitas projects.  For the cloned Stack Overflow snippets, the
average ratio of cloned code for $S_D$, $S_E$, $N_D$, and $N_E$ is
38\%, 50\%, 30\%, and 33\% respectively.
% A quick manual check of Simian's clone report revealed that there
% were 11 problematic snippets. These 11 snippets triggered Simian to
% generate large clone clusters containing a huge number of false
% clones from array initialisation. Hence, their clones were removed
% from further analyses.

@@

\begin{table}
\caption{Investigated online clone pairs and corresponding snippets
  and Qualitas projects for the different data sets}
\label{tab:snippets}
\centering
\begin{tabular}{l|rrrr}
  \hline 
  Data Set & Pairs & Snippets & Projects & Avg.~C$_{\textrm{\textit{\%}}}$ \\
  \hline 
  \multicolumn{4}{l}{\textit{Reported Clones}} \\
  \hline
  $S_D$ & 67,570 & 1,086 & 92 & 38\% \\
  $S_E$ & 63,635,844 & 1,531 & 111 & 50\% \\
  $N_D$ & 632,855& 1,392 & 82 & 30\% \\
  $N_E$ & 251,449,849& 12,886 & 88 & 33\% \\
  \hline
  Total & 315,786,118 & &\\
  \hline
  \multicolumn{4}{l}{\textit{Filtered Data Sets}} \\
  \hline
  \textit{good} & 2,308 & 92 & 66 & 23\% \\
  \textit{ok'} & 11,749 & 136 & 39 & 28\% \\
  $S_D'$ & 17,081 & 471 & 76 & 31\% \\
  $N_D'$ & 88 & 77 & 29 & 26\% \\
  \hline
  Total & 31,946 & 621 & 95 & 27\%\\
  \hline 
  \multicolumn{4}{l}{\textit{True Positives without AC}} \\
  \hline 
  $\textit{good}/\textrm{AC}$ & 136 & 47 & 25 & 23\% \\
  $\textit{ok'}/\textrm{AC}$ & 11,644 & 125 & 34 & 28\% \\
  $S_D'/\textrm{AC}$ & 17,673 & 448 & 72 & 31\% \\
  $N_D'/\textrm{AC}$ & 75 & 44 & 17 & 28\% \\
  \hline
  Total & 29,528 & 555 & 81 & 28\% \\
  \hline
\end{tabular}
\end{table}

However, using Bellon's criteria for matching clone pairs, only
0.1\textperthousand~of all pairs are agreed by two tool/configuration
combinations. As shown in \Cref{tab:snippets}, for the 2,308
\textit{good} pairs, there are 92 Stack Overflow snippets which are
associated with 66 Qualitas projects. The 11,749 \textit{ok'} pairs
are clones between 136 Stack Overflow snippets and 39 Qualitas
projects.  Moreover, for the disagreed pairs, we found 17,081 clone
pairs reported by $S_D'$ are clones between 471 Stack Overflow
snippets and 76 Qualitas projects and 88 $N_D'$ clone pairs are clones
between 77 Stack Overflow snippets and 29 Qualitas projects. In total
we found that the filtered data sets contains 31,946 clone pairs which
are clones between 621 Stack Overflow snippets and 95 Qualitas
projects. During the manual investigation, we identified 2,418 pairs
as being accidential clones (AC), i.e.~false positives. After removing
them, the data set still contains 29,528 clone pairs between 555 Stack
Overflow snippets and 81 Qualitas projects.

\textbf{To answer RQ1, we found most Qualitas projects to share
  similar code with Stack Overflow code snippets. Depending on the
  data set, between 82 to all 111 projects share similar code. The
  filtered data set has 95 projects share code with Stack
  Overflow. Even in the manually confirmed data set of 29,528 clone
  pairs, a majority of 81 Qualitas projects share similar code with
  Stack Overflow.}
